**Title:** Analyzing long-term water quality of lakes in Rhode Island and the Northeastern United States with an anomaly approach

### 2020-12-02 manuscript/ecosphere_resubmit_2/manuscript.Rmd
text revisions complete.  Now on to figure/tables.

```{r analysis, include=FALSE, cache=TRUE}
source(here::here("R/data_clean.R"), encoding = "UTF-8")
source(here::here("R/data_available.R"), encoding = "UTF-8") 
source(here::here("R/summary_stats.R"), encoding = "UTF-8")  
source(here::here("R/figures_anomaly_only.R"), encoding = "UTF-8")
```

@@

<!-- Jeff start here for change to comment #4 -->
Add Paragraph about RI lakes: Context about human pressures on RI lakes + one sentence about adequate data being available

>>>>

```{r analysis, include=FALSE, cache=TRUE}
source(here::here("R/data_clean.R"), encoding = "UTF-8")
source(here::here("R/data_available.R"), encoding = "UTF-8") 
source(here::here("R/summary_stats.R"), encoding = "UTF-8")  
source(here::here("R/figures_anomaly_only.R"), encoding = "UTF-8")
source(here::here("R/ri_stats.R"), encoding = "UTF-8")
```

@@

In this study, we focus on the state of Rhode Island for several reasons.  Rhode Island has the second highest population density in the country, yet still has a mix of land use/land cover with developed areas making up ~`r ri_nlcd_data$lulc_perc[ri_nlcd_data$nlcd_class_1 == "Development"]`% of the state, forested areas ~`r ri_nlcd_data$lulc_perc[ri_nlcd_data$nlcd_class_1 == "Forest"]`%, wetlands ~`r ri_nlcd_data$lulc_perc[ri_nlcd_data$nlcd_class_1 == "Wetlands"]`%, and agriculture ~`r ri_nlcd_data$lulc_perc[ri_nlcd_data$nlcd_class_1 == "Planted/Cultivated"]`%.  Given these facts, Rhode Island lakes occur across a gradient of land use/land cover and face a suite of human pressures that most lakes in the nation are also facing with nutrients and pathogens of particular concern in the state [@ri_2016_waterquality].  Lastly, Rhode Island provides an ideal study area as significant, long-term datasets are available for lakes making it possible to examine water quality trends.
